Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{ Funded by DARPA Cyber Assured Systems Engineering (CASE) contract HR00111890001. }

### 2021-05-07 paper/synthesis.tex
Restructure tex files

\subsection{Filters}
\subsection{Monitors}
\subsection{Gates}

>>>>

A \emph{system} is a collection of \emph{components}, \emph{connections} between components, a \emph{scheduler} to order execution, and a \emph{system environment} for primary inputs. The computation for the component in this work is defined entirely by a step function:
\[
\konst{stepFn} : \mathit{input} \times \mathit{stateVars} \to \mathit{stateVars} \times \mathit{output}
\]
The scheduler \emph{activates} components in some order. Activating a component is defined as follows: 
\[
\begin{array}{ll}
 \mathit{(i_1,\ldots)} & = \konst{readInputs}(); \\
 (v_1,\ldots) & = \konst{readState}() ; \\
 ({v_1}',\ldots), ({o_1}',\ldots) & = \konst{stepFn} ((i_1,\ldots),(v_1,\ldots)) ; \\
 \multicolumn{2}{l}{\konst{writeState}({v_1}',\ldots);} \\
 \multicolumn{2}{l}{\konst{writeOutputs}({o_1}'\ldots);} \\
\end{array}
\]
It is assumed that the scheduler follows some sensible partial order of component activation and allows each component sufficient time for its computation.

### 2021-05-07 paper/system.tex
Restructure tex files

An environment, $\theta: \lval \mapsto \konst{string}$ binds L-values to strings. $\Delta : \konst{string} \to \mathbb{N}$ binds constant names to numbers. Functions $\konst{toN}:\konst{string}\to\mathbb{N}$ and $\konst{toB}:\konst{string}\to\konst{bool}$ interpret byte sequences to numbers and booleans, respectively.

The well-formed assumption enables the use of a single global environment for the semantics. The semantics are synchronous data-flow on a single clock defined over a sequences of environments where $\theta^i$ is the $i^\mathrm{th}$ environment in the stream. Expression evaluation is defined in the context of this environment stream as shown is \figref{fig:eval}. Here, $\konst{eval}\; i\; e$ carries with it the index of the environment to be used for the expression.

@@

The meaning of the specification is a set of finite environment streams where the guarantees hold at each step of the streams and the updated mappings or the \konst{eq}-statements are consistent with the statements.

At the $i^\mathrm{th}$ step of the stream, $\theta^i$

Each \emph{step} of the specification updates a corresponding environment in the stream making it complete at the end of the step.

The environments in the stream are partial containing only mappings for inputs.

\begin{comment}
  A \emph{system} is a collection of \emph{components}, \emph{connections} between components, a \emph{scheduler} to order execution, and a \emph{system environment} for primary inputs. The computation for the component in this work is defined entirely by a step function:
\[
\konst{stepFn} : \mathit{inports} \times \mathit{stateVars} \to \mathit{stateVars}
\]
The scheduler \emph{activates} components in some order. Activating a component is defined as follows: 
\[
\begin{array}{ll}
 \mathit{inportVals} & = \konst{readInputs}(); \\
 (v_1,\ldots,v_k) & = \konst{readState}() ; \\
 ({v_1}',\ldots,{v_k}') & = \konst{stepFn} (\mathit{inportVals},\mathit{stateVars}) ; \\
 \multicolumn{2}{l}{\konst{writeState}({v_1}',\ldots,{v_k}');} \\
 \multicolumn{2}{l}{\konst{writeOutputs}({v_1}',\ldots,{v_k}');} \\
\end{array}
\]
It is assumed that the scheduler follows some sensible partial order of component activation and allows each component sufficient time for its computation.
\end{comment}

>>>>

An environment, $\theta: \lval \mapsto \konst{string}$ binds L-values to strings.

The well-formed assumption enables the use of a single global environment for the semantics. The semantics are synchronous data-flow on a single clock defined over a sequences of environments where $\theta^i$ is the $i^\mathrm{th}$ environment in the stream. Expression evaluation is defined in the context of this environment stream as shown is \figref{fig:eval}. Here, $\konst{eval}\; i\; e$ carries with it the index of the environment to be used for the expression. $\Delta : \konst{string} \to \mathbb{N}$ binds constant names to numbers. Functions $\konst{toN}:\konst{string}\to\mathbb{N}$ and $\konst{toB}:\konst{string}\to\konst{bool}$ interpret byte sequences to numbers and booleans, respectively.

@@
